\chapter{EXPLOITING HUMAN VARIANTS
IN GENOMICS STUDIES}

WHY TO USE SNPs?
features to maximize distinguishing the individuals of a population. different values for different

MAF cannot be over 0.5, as we suppose two possible variants alleles

genetic fingerprinting
- combination of char individual char
 SNPs the easier way.
 how to compute a measure?
 those representing different ethnicity
BUILD A DISTANCE
	1- concordance (1 different site, 0 equal
	goes from 0 to 1 (1 is not completely possible)
	
	- FIGURE
	average distance increases if subsample of less SNPs
	augment standard deviation
	20 SNPs 
	selecting random number of SNP and 
	
	
SNPS have a unique identifier, which can be used to search for informations about the SNPs

EXERCISE

loss of heterozygosity is associated to tumors in general, as the loss of an allele makes heterozigous characteristics to be not heterozigous anymore.
This type of knowledge could be used to understand clonality and subclonality, as you expect patterns in loss of heterozigosity.

\chapter{Ethnicity}
genetic structure of human population, think about variants
know genetic structure and substructures of data

- HAPMAP
	
through PCA, it is possible to divide the samples in a 2D space 
start thinking about grouping

- PAPER
500k SNPs, informations origin grandparents and geographic location.
they found it was possible to distinguish in an optimal way geographic locations.
distinguish individuals from Spain, Italy. Higher densities related to sampling ?
it could be possible to distinguish populations of different cantones in Switzerland.
geographical clusters expected 
genetic structure has to be taken into consideration to avoid sporious results.


